Constant-round Blind Classical Verification of Quantum Sampling

### 2021-06-02 acknowledgements.tex
Sync for submission

\section{Acknowledgments}

\Ethan{TODO Acknowledge Morimae}

\Ethan{TODO Acknowledge STOC Reviewer for bringing up Brakerski's QFHE}

>>>>

\section*{Acknowledgments}

The authors would like to thank Tomoyuki Morimae for valuable feedback that helped improve the paper.
We are also thankful to the anonymous reviewers from STOC 2021 for various useful comments and mentioning the stronger security guarantees given by Brakerski's encryption scheme in \cite{brakerski_qfhe}. \Ethan{check if this is ok}

### 2021-06-02 blind.tex
Sync for submission

However, several issues need to be taking care to make the idea work. First, since the verifier is classical, we need the quantum homomorphic encryption scheme $\QHE$ to be \emph{classical friendly} as defined in Definition~\ref{def:classical-friendly}. Namely, the key generation algorithm and the encryption algorithm for classical messages should be classical, and when the underlying message is classical, the ciphertext (potentially from homomorphic evaluation) and the decryption algorithm should be classical as well. Fortunately, the quantum homomorphic encryption scheme of Mahadev~\cite{mahadev_qfhe} is classical friendly.

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{thm} \label{thm:compiler-blindness}
    Assuming the QLWE assumption, $\Piblind$ is blind.
\end{thm}
\begin{proof}
    We show that for all cheating $\BQP$ prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
    $P^*$ cannot distinguish $(P^*, \Vblind(x))(1^\lambda)$ from $(P^*, \Vblind(0^n))(1^\lambda)$ with noticeable probability in $\lambda$.
    We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(1^\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(1^\lambda)$.
    For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
    except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
    We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ under $pk_1$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
    We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.

@@

\begin{thm}
    Assuming the QLWE assumption, \Ethan{wording sounds awkward? Maybe ``under the QLWE assumption"...?} there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
\end{thm}

\begin{thm}
        Assuming the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
\end{thm}

>>>>

However, several issues need to be taking care to make the idea work. First, since the verifier is classical, we need the quantum homomorphic encryption scheme $\QHE$ to be \emph{classical friendly} as defined in Definition~\ref{def:classical-friendly}. Namely, the key generation algorithm and the encryption algorithm for classical messages should be classical, and when the underlying message is classical, the ciphertext (potentially from homomorphic evaluation) and the decryption algorithm should be classical as well. Fortunately, the quantum homomorphic encryption scheme of Mahadev~\cite{mahadev_qfhe} and Brakerski~\cite{brakerski_qfhe} are classical friendly. Moreover, Brakerski's scheme requires a weaker QLWE assumption, where the modulus is polynomial instead of super-polynomial.

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{thm} \label{thm:compiler-blindness}
    Under the QLWE assumption with polynomial modulus, $\Piblind$ is blind.
\end{thm}
\begin{proof}
    We show that for all cheating $\BQP$ prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
    $P^*$ cannot distinguish $(P^*, \Vblind(x))(1^\lambda)$ from $(P^*, \Vblind(0^n))(1^\lambda)$ with noticeable probability in $\lambda$.
    We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(1^\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(1^\lambda)$.
    For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
    except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
    We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ under $pk_1$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
    We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.

@@

\begin{thm}
    Under the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
\end{thm}

\begin{thm}
        Under the QLWE assumption, there exists a blind, four-message $\QPIP_0$ protocol for all sampling problems in $\SampBQP$ with negligible completeness error and computational soundness.
\end{thm}

### 2021-06-02 hamiltonian.tex
Sync for submission

\subsection{Reducing $\SampBQP$ to the X-Z Local Hamiltonian} \label{sec:LHXZ}
As we mentioned in this introduction, we will employ the circuit \emph{history} state in the original construction of the Local Hamiltonian problem~\cite{kitaev2002classical} to encode the circuit information for $\SampBQP$.
However, there are distinct requirements between certifying the computation for $\BQP$ and $\SampBQP$ based on the history state.
For any quantum circuit $C$ on input $x$, the original construction for certifying $\BQP$\footnote{The original construction is for the purpose of certifying problems in QMA. We consider its simple restriction to problems inside BQP.} consists of local Hamiltonian $\Hin, \Hclock, \Hprop$, $\Hout$ where $\Hin$ is used to certify the initial input $x$, $\Hclock$ to certify the validness of the clock register,  $\Hprop$ to certify the gate-by-gate evolution according to the circuit description, and $\Hout$ to certify the final output.
In particular, the corresponding history state is in the ground space of $\Hin$, $\Hclock$, and $\Hprop$. Note that $\BQP$ is a decision problem and its outcome (0/1) can be easily encoded into the energy $\Hout$ on the single output qubit.
As a result, the outcome of $\BQP$ can simply be encoded by the \emph{ground energy} of $\Hin + \Hclock+\Hprop + \Hout$.

To deal with $\SampBQP$, we will still employ $\Hin, \Hclock$, and $\Hprop$ to certify the circuit's input, the clock register, and gate-by-gate evolution. However, in $\SampBQP$, we care about the entire final state of the circuit, rather than the energy on the output qubit.
%The history state remains in the ground space of $\Hin + \Hprop$.  
Our approach to certify the entire final state (which is encoded inside the history state) is to make sure that the history state is the unique ground state of $\Hin + \Hclock+ \Hprop$ and all other orthogonal states will have much higher energies.
Namely, we need to construct some $\Hin'+ \Hclock'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies.
It is hence guaranteed that any state with close-to-ground energy must also be close to the history state.
We remark that this is a different requirement from most local Hamiltonian constructions that focus on the ground energy.
We achieve so by using the \emph{perturbation} technique developed in~\cite{kempe_kitaev_regev_2006} for reducing the locality of Hamiltonian.
Another example of local Hamiltonian construction with a focus on the spectral gap can be found in~\cite{adiabatic}, where the purpose is to simulate quantum circuits by adiabatic quantum computation.

We need two more twists for our purpose.
First, as we will eventually measure the final state in order to obtain classical samples, we need that the final state occupies a large fraction of the history state. We can simply add dummy identity gates.
Second, as we are only able to perform $X$ or $Z$ measurement by techniques from~\cite{FOCS:Mahadev18a},
we need to construct X-Z only local Hamiltonians.
Indeed, this has been shown possible in, e.g.,~\cite{PhysRevA.78.012352}, which serves as the starting point of our construction.

>>>>

\subsection{Reducing $\SampBQP$ to the X-Z Local Hamiltonian} \label{sec:LHXZ}

### 2021-06-02 hamiltonian_short.tex
Sync to GitHub for 1st submission
Sync for submission

See \Cref{sec:sampbqp} for the details of the construction of our $\QPIP_1$ Protocol for $\SampBQP$, \Cref{ProtoQPIP1}. The soundness and completeness of \Cref{ProtoQPIP1} is stated in the following theorem.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem\\ $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound.\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.}
	%\XW{do we want precise error bound?}
\end{thm}

>>>>

As we mentioned in this introduction, we will employ the circuit \emph{history} state in the original construction of the Local Hamiltonian problem~\cite{kitaev2002classical} to encode the circuit information for $\SampBQP$.
However, there are distinct requirements between certifying the computation for $\BQP$ and $\SampBQP$ based on the history state.
For any quantum circuit $C$ on input $x$, the original construction for certifying $\BQP$\footnote{The original construction is for the purpose of certifying problems in QMA. We consider its simple restriction to problems inside BQP.} consists of local Hamiltonian $\Hin, \Hclock, \Hprop$, $\Hout$ where $\Hin$ is used to certify the initial input $x$, $\Hclock$ to certify the validness of the clock register,  $\Hprop$ to certify the gate-by-gate evolution according to the circuit description, and $\Hout$ to certify the final output.
In particular, the corresponding history state is in the ground space of $\Hin$, $\Hclock$, and $\Hprop$. Note that $\BQP$ is a decision problem and its outcome (0/1) can be easily encoded into the energy $\Hout$ on the single output qubit.
As a result, the outcome of $\BQP$ can simply be encoded by the \emph{ground energy} of $\Hin + \Hclock+\Hprop + \Hout$.

To deal with $\SampBQP$, we will still employ $\Hin, \Hclock$, and $\Hprop$ to certify the circuit's input, the clock register, and gate-by-gate evolution. However, in $\SampBQP$, we care about the entire final state of the circuit, rather than the energy on the output qubit.
%The history state remains in the ground space of $\Hin + \Hprop$.  
Our approach to certify the entire final state (which is encoded inside the history state) is to make sure that the history state is the unique ground state of $\Hin + \Hclock+ \Hprop$ and all other orthogonal states will have much higher energies.
Namely, we need to construct some $\Hin'+ \Hclock'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies.
It is hence guaranteed that any state with close-to-ground energy must also be close to the history state.
We remark that this is a different requirement from most local Hamiltonian constructions that focus on the ground energy.
We achieve so by using the \emph{perturbation} technique developed in~\cite{kempe_kitaev_regev_2006} for reducing the locality of Hamiltonian.
Another example of local Hamiltonian construction with a focus on the spectral gap can be found in~\cite{adiabatic}, where the purpose is to simulate quantum circuits by adiabatic quantum computation.

We need two more twists for our purpose.
First, as we will eventually measure the final state in order to obtain classical samples, we need that the final state occupies a large fraction of the history state. We can simply add dummy identity gates.
Second, as we are only able to perform $X$ or $Z$ measurement by techniques from~\cite{FOCS:Mahadev18a},
we need to construct X-Z only local Hamiltonians.
Indeed, this has been shown possible in, e.g.,~\cite{PhysRevA.78.012352}, which serves as the starting point of our construction.

 For more details of the construction of our $\QPIP_1$ Protocol for $\SampBQP$, \Cref{ProtoQPIP1}, see \Cref{sec:sampbqp}. The soundness and completeness of \Cref{ProtoQPIP1} is stated in the following theorem.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ is a $\QPIP_1$ protocol for the $\SampBQP$ problem\\ $(D_x)_{x\in\set{0,1}^*}$ with negligible completeness error and is statistically sound\footnote{The soundness and completeness of a $\SampBQP$ protocol is defined in \Cref{dfn:stats-secure-proto-sampbqp}.} where the verifier only needs to do non-adaptive $X/Z$ measurements.
	%\XW{do we want precise error bound?}	
\end{thm}

### 2021-06-02 introduction.tex
Sync for submission

Another desirable property of CVQC protocols is  \emph{blindness}, which means that the prover does not learn any information about the private input for the delegated computation.\footnote{In literature, the definition of blindness may also require to additionally hide the computation. We note the two notions are equivalent from a feasibility point of view by a standard transformation (see Remark~\ref{} in Section~\ref{}\hannote{missing}). 
%The two notions are equivalent from a feasibility point of view by a standard transformation that takes the description of the computation as part of the input and delegate the computation of  universal quantum circuits.
} In the relaxed setting where the verifier has a limited quantum capability, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed a blind $\QPIP_1$ protocol for delegating quantum computation with information-theoretic security that also handles sampling problems. 
%
However, for purely classical verifiers, blind CVQC protocols seem much more difficult to construct. This goal is recently achieved by the seminal work of Gheorghiu and Vidick~\cite{FOCS:GheVid19}, who constructed the first blind CVQC protocol for $\BQP$ by constructing a composable remote state preparation protocol and combining it with the verifiable blind quantum computation protocol of Fitzsimons and Kashefi~\cite{FK17}. However, their protocol has   polynomially many rounds  and requires a rather involved analysis. Before our work, it is an open question whether constant-round blind CVQC protocol for $\BQP$ is achievable.

\paragraph{Our Contribution.} Somewhat surprisingly, we provide a simple yet powerful  
\emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving completeness, soundness, as well as its round complexity. 
Our compiler relies on quantum fully homomorphic encryption (QFHE) schemes with certain ``classical-friendly'' properties, which is satisfied by both constructions of Mahadev~\cite{mahadev_qfhe} and Brakerski~\cite{??}.

@@

@@

%As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. 
\begin{theorem}[informal]
        Assuming the QLWE assumption, there exists a blind, four-message CVQC protocol for all sampling problems in $\SampBQP$ with  computational soundness and negligible completeness error.
\end{theorem}

\paragraph{Techniques.} At a high-level, the idea is simple: we run the original protocol under a QFHE with the QFHE key generated by the verifier. Intuitively, this allows the prover to compute his next message under encryption without learning verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
One subtlety with this approach is the fact that the verifier is classical while the QFHE cipher text could contain quantum data.
In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical. Fortunately, such  ``classical-friendly'' property is satisfied by the construction of~\cite{mahadev_qfhe,??}.

@@

\paragraph{On the Inverse Polynomial Error in $\SampBQP$.} To be added. \KM{where to add this? Sec 1.3?}

>>>>

Another desirable property of CVQC protocols is  \emph{blindness}, which means that the prover does not learn any information about the private input for the delegated computation.\footnote{In literature, the definition of blindness may also require to additionally hide the computation. We note the two notions are equivalent from a feasibility point of view by a standard transformation (see Remark~\ref{rmk:blind-comp} in Section~\ref{sec:qpip_def}). 
%The two notions are equivalent from a feasibility point of view by a standard transformation that takes the description of the computation as part of the input and delegate the computation of  universal quantum circuits.
} In the relaxed setting where the verifier has a limited quantum capability, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed a blind $\QPIP_1$ protocol for delegating quantum computation with information-theoretic security that also handles sampling problems. 
%
However, for purely classical verifiers, blind CVQC protocols seem much more difficult to construct. This goal is recently achieved by the seminal work of Gheorghiu and Vidick~\cite{FOCS:GheVid19}, who constructed the first blind CVQC protocol for $\BQP$ by constructing a composable remote state preparation protocol and combining it with the verifiable blind quantum computation protocol of Fitzsimons and Kashefi~\cite{FK17}. However, their protocol has   polynomially many rounds  and requires a rather involved analysis. Before our work, it is an open question whether constant-round blind CVQC protocol for $\BQP$ is achievable.

\paragraph{Our Contribution.} Somewhat surprisingly, we provide a simple yet powerful  
\emph{generic}  compiler that transforms any CVQC protocol to a blind one while preserving completeness, soundness, as well as its round complexity. 
Our compiler relies on quantum fully homomorphic encryption (QFHE) schemes with certain ``classical-friendly'' properties, which is satisfied by both constructions of Mahadev~\cite{mahadev_qfhe} and Brakerski~\cite{brakerski_qfhe}.

@@

\begin{theorem}[informal]
    Under the QLWE assumption, there exists a blind, four-message CVQC protocol for all languages in $\BQP$ with negligible completeness and soundness errors.
\end{theorem}

@@

%As a simple corollary of combining both results above, we achieve a constant-round blind CVQC protocol for $\SampBQP$. 
\begin{theorem}[informal]
        Under the QLWE assumption, there exists a blind, four-message CVQC protocol for all sampling problems in $\SampBQP$ with  computational soundness and negligible completeness error.
\end{theorem}

\paragraph{Techniques.} At a high-level, the idea is simple: we run the original protocol under a QFHE with the QFHE key generated by the verifier. Intuitively, this allows the prover to compute his next message under encryption without learning verifier's message, and hence achieves blindness while preserving the properties of the original protocol.
One subtlety with this approach is the fact that the verifier is classical while the QFHE cipher text could contain quantum data.
In order to make the classical verifier work in this construction, the ciphertext and the encryption/decryption algorithm need to be classical when the underlying message is classical. Fortunately, such  ``classical-friendly'' property is satisfied by the construction of~\cite{mahadev_qfhe, brakerski_qfhe}.

@@

\subsection{Related Works and Discussions}  \label{subsec:discussion}

As mentioned, while we are the first to explicitly investigate delegation of quantum sampling problems, Hayashi and Morimae~\cite{hayashi2015verifiable} constructed an one-round blind $\QPIP_1$ protocol that can be used to delegate $\SampBQP$ and achieve our notion of information-theoretical security. Like our $\SampBQP$ protocol, their protocol has an arbitrarily small inverse polynomial soundness error instead of negligible soundness error. Also as mentioned,  Gheorghiu and Vidick~\cite{FOCS:GheVid19} extends Mahadev's techniques to obtain a blind CVQC protocol. The protocol of \cite{FOCS:GheVid19} has polynomially many rounds, whereas our protocol has 4 rounds.

It is also worth noting that several existing constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) can be generalized to delegate $\SampBQP$ in a natural way, but it seems challenging to analyze the soundness of the generalized protocol. Furthermore, it is highly likely that these generalized protocols cannot achieve negligible soundness error for $\SampBQP$. The reason is that in all these constructions, some form of cut and choose are used to achieve soundness.\Ethan{Maybe unnecessary?: , and for delegating decision problems, negligible soundness can be achieved by taking majority vote of multiple outcomes.} For sampling problems, as mentioned, there seems to be no generic way to combine multiple samples for error reduction, so the verifier needs to choose one sample to output in the cut and choose. In this case, an adversarial prover may choose to cheat on a random copy in the cut and choose and succeed in cheating with an inverse polynomial probability.

On the other hand, while the definition of $\SampBQP$ in~\cite{aaronson_2013, Boson} allows an inverse polynomial error, there seems to be no fundamental barriers to achieve negligible error. It is conceivable that negligible error can be achieved using quantum error correction. Negligible error is naturally desirable and achievable in the related setting of secure multi-party quantum computation (MPQC\hannote{ref})\footnote{In MPQC, for the special case where the output is classical, it has the same simulation-based security for the output as our soundness definition.}. There, it\hannote{?} is achieved by using either verifiable quantum secret sharing or quantum authentication codes, both of which requires quantum communications. An intriguing open problem is whether it is possible to achieve negligible soundness error with classical communication while delegating a quantum sampling problem.

%while a classical verifier is delegating a quantum sampling problem.

%\paragraph{On the Inverse Polynomial Error in $\SampBQP$.}
%To be added. \KM{where to add this? Sec 1.3?}

### 2021-06-02 model.tex
Sync for submission

To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems. We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) may be generalized naturally to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the soundness property we just defined. Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question. %We also note that

>>>>

%To the best of our knowledge, we are the first to formally define delegation of quantum sampling problems. We also note that while several constructions in the relaxed models (e.g., verifiable blind computation~\cite{FK17}) may be generalized naturally to delegate quantum sampling problem and allow the verifier to learn multi-bit outputs, it seems non-trivial to show that these constructions achieve the soundness property we just defined. Proving the soundness of these constructions for delegating $\SampBQP$ is an interesting open question. %We also note that

### 2021-06-02 paper.tex
Add acknowledgements section
Sync for submission

\author[1]{Kai-Min Chung\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}. Partially supported by the 2019 Academia Sinica Career Development Award under Grant no. 23-17, and MOST QC project under Grant no. MOST 108-2627-E-002-001.}}
\author[2]{Yi Lee\thanks{\href{mailto:ylee1228@umd.edu}{ylee1228@umd.edu}. This work was done while affiliated to Academia Sinica and to National Taiwan University.}}
\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}. Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense.}}
\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER).}}
\affil[1]{Institute of Information Science, Academia Sinica, Taiwan}
\affil[2]{Department of Computer Science, University of Maryland, USA}
\affil[3]{Department of Computer Science, National Tsing Hua University, Taiwan}
\affil[4]{
	Department of Computer Science, Institute for Advanced Computer Studies,
	and Joint Center for Quantum Information and Computer Science,
	University of Maryland, USA
}

@@

>>>>

\author[1]{Kai-Min Chung\thanks{\href{mailto:kmchung@iis.sinica.edu.tw}{kmchung@iis.sinica.edu.tw}. Partially supported by the 2019 Academia Sinica Career Development Award under Grant no. 23-17, and MOST QC project under Grant no. MOST 108-2627-E-002-001.}}
\author[2]{Yi Lee\thanks{\href{mailto:ylee1228@umd.edu}{ylee1228@umd.edu}. This work was done while affiliated to Academia Sinica and to National Taiwan University.}}
\author[3]{Han-Hsuan Lin\thanks{\href{mailto:linhh@cs.nthu.edu.tw}{linhh@cs.nthu.edu.tw}. Part of this work was done while supported by Scott Aaronson's Vannevar Bush Faculty Fellowship from the US Department of Defense. Partially funded by MOST Grant no. 110-2222-E-007-002-MY3}}
\author[4]{Xiaodi Wu\thanks{\href{mailto:xwu@cs.umd.edu}{xwu@cs.umd.edu}. Partially supported by the U.S. National Science Foundation grant CCF-1755800, CCF-1816695, and CCF-1942837 (CAREER). }}
\affil[1]{Institute of Information Science, Academia Sinica, Taiwan}
\affil[2]{Department of Computer Science, University of Maryland, USA}
\affil[3]{Department of Computer Science, National Tsing Hua University, Taiwan}
\affil[4]{
	Department of Computer Science, Institute for Advanced Computer Studies,
	and Joint Center for Quantum Information and Computer Science,
	University of Maryland, USA
}

@@

\input{acknowledgements}

### 2021-06-02 preliminaries.tex
Sync for submission

@@

\begin{definition} \label{def:classical-friendly}
    we call a quantum homomorphic encryption scheme \emph{classical-friendly} if it has the following properties:
    \begin{itemize}
        \item $\QGen$ is a classical algorithm
        \item In the case where the plaintext is classical, $\QEnc$ can be done classically.
        \item When the underlying message is classical, the corresponding ciphertext is also classical and can be decrypted classically.
    \end{itemize}
\end{definition}

>>>>

\begin{remark} \label{rmk:blind-comp}
In literature, the definition of blindness may also require to additionally hide the computation. The two notions are equivalent from a feasibility point of view by a standard transformation (e.g., as in~\cite{GHRW14} in a different context) that takes the description of the computation as part of the input and delegate the computation of  universal quantum circuits.
\end{remark}

@@

\begin{definition} \label{def:classical-friendly}
    we call a quantum homomorphic encryption scheme \emph{classical-friendly} if it has the following properties:
    \begin{itemize}
        \item $\QGen$ is a classical algorithm
        \item In the case where the plaintext is classical, $\QEnc$ can be done classically.
        \item When the underlying message is a classical-quantum state, then the cipher text is composed of a corresponding classical part and a corresponding quantum part. Moreover, the classical part has a classical ciphertext and can be decrypted classically.
    \end{itemize}
\end{definition}

### 2021-06-02 qpip.tex
Sync for submission

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $(m+1)$-fold tensor products of identical copies of some states $\tau_j$.
	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
	such that for all quantum-classical channels $\Lambda_i$ acting on registers of size $s$:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}_1
	\leq\sqrt{\frac{2m^2s}{M-m}}
	\leq\frac{\eps}{6},$$
	where $\sigma'_{\leq m+1}$ is the first $m+1$ registers of $\sigma'$.
	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
	$\Lambda_{m+1}$ measures the data register under the standard basis.

>>>>

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma'$ with the measurement result of a classical mix over $(m+1)$-identical copies of some states $\tau_j$.
	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
	such that for all quantum-classical channels $\Lambda_i$ acting on $s$-qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}_1
	\leq\sqrt{\frac{2m^2s}{M-m}}
	\leq\frac{\eps}{6},$$
	where $\sigma'_{\leq m+1}$ is the first $m+1$ registers of $\sigma'$.
	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
	$\Lambda_{m+1}$ measures the data register under the standard basis.
